Smoothing seismicity techniques applied to seismic source characterization and probabilistic seismic hazard analysis in Brazil

### 2015-02-19 manuscript.tex
add figures, change tables, pre-round03

% \documentclass[draft, grl]{agutex}
\documentclass[grl]{agutex}

@@

\begin{figure}
	\begin{center}
	\begin{table}[H]
		\begin{tabular}{ p{0.25\textwidth}
						 p{0.25\textwidth}
						 p{0.25\textwidth}
						 p{0.25\textwidth} }
		\footnotesize(a) &
		\footnotesize(b) &
		\footnotesize(c) &
		\footnotesize(d)
		\\
		\includegraphics[height=4cm]{z_img_2dhist_assump_25}  &
		\includegraphics[height=4cm]{z_img_f_assump_50_25} &
		\includegraphics[height=4cm]{z_img_f_assump_150_025} &
		\includegraphics[height=4cm]{z_img_woo_assump_25} 
		\\
		\footnotesize(e) &
		\footnotesize(f) &
		\footnotesize(g) &
		\footnotesize(h)
		\\
		\includegraphics[height=4cm]{z_img_2dhist_stepp_25}  &
		\includegraphics[height=4cm]{z_img_f_stepp_50_025} &
		\includegraphics[height=4cm]{z_img_f_stepp_150_025} &
		\includegraphics[height=4cm]{z_img_woo_stepp_25} 
		\\
		\footnotesize(i) &
		\footnotesize(j) &
		\footnotesize(l) &
		\footnotesize(m)
		\\
		\includegraphics[height=4cm]{z_img_2dhist_assump_50}  &
		\includegraphics[height=4cm]{z_img_f_assump_50_50} &
		\includegraphics[height=4cm]{z_img_f_assump_150_050} &
		\includegraphics[height=4cm]{z_img_woo_assump_50} 
		\\
		\footnotesize(n) &
		\footnotesize(o) &
		\footnotesize(p) &
		\footnotesize(q)
		\\
		\includegraphics[height=4cm]{z_img_2dhist_stepp_50}  &
		\includegraphics[height=4cm]{z_img_f_stepp_50_050} &
		\includegraphics[height=4cm]{z_img_f_stepp_150_050} &
		\includegraphics[height=4cm]{z_img_woo_stepp_50}

@@

\begin{table}[H]
	\caption{Temporal completeness comparision. For each magnitude interval,
	the completess was computed by the \citet{stepp_1972} method and the respective assigned value.}
	\begin{tabular}{c c c}
		\hline
	\textbf{magnitude} & \textbf{year (Stepp)} & \textbf{year (simplest)} \\
		\hline
		2.0 & 1982 	& 1885 \\
		2.5 & 1980 	& 1965 \\
		3.0 & 1976 	&  \\
		3.5 & 1969 	& 1960 \\
		4.0 & 1955 	&  \\
		4.5 &  		& 1935 \\
		5.0 & 1952 	&  \\
		5.5 & 1927 	&  \\
		6.0 &  		&  \\
		6.5 &  		&  \\
		\hline
	\end{tabular}
	\label{tab:completeness}
\end{table}

>>>>

\documentclass[draft, grl]{agutex}
% \documentclass[grl]{agutex}

@@

\begin{figure}
	\begin{center}
	\begin{table}[H]
		\begin{tabular}{ p{0.25\textwidth}
						 p{0.25\textwidth}
						 p{0.25\textwidth}
						 p{0.25\textwidth} }
		\footnotesize(a) &
		\footnotesize(b) &
		\footnotesize(c) &
		\footnotesize(d)
		\\
		\includegraphics[height=4cm]{z_img_2dhist_assump_25}  &
		\includegraphics[height=4cm]{z_img_f_assump_50_25} &
		\includegraphics[height=4cm]{z_img_f_assump_150_25} &
		\includegraphics[height=4cm]{z_img_woo_assump_25} 
		\\
		\footnotesize(e) &
		\footnotesize(f) &
		\footnotesize(g) &
		\footnotesize(h)
		\\
		\includegraphics[height=4cm]{z_img_2dhist_stepp_25}  &
		\includegraphics[height=4cm]{z_img_f_stepp_50_25} &
		\includegraphics[height=4cm]{z_img_f_stepp_150_25} &
		\includegraphics[height=4cm]{z_img_woo_stepp_25} 
		\\
		\footnotesize(i) &
		\footnotesize(j) &
		\footnotesize(l) &
		\footnotesize(m)
		\\
		\includegraphics[height=4cm]{z_img_2dhist_assump_50}  &
		\includegraphics[height=4cm]{z_img_f_assump_50_50} &
		\includegraphics[height=4cm]{z_img_f_assump_150_50} &
		\includegraphics[height=4cm]{z_img_woo_assump_50} 
		\\
		\footnotesize(n) &
		\footnotesize(o) &
		\footnotesize(p) &
		\footnotesize(q)
		\\
		\includegraphics[height=4cm]{z_img_2dhist_stepp_50}  &
		\includegraphics[height=4cm]{z_img_f_stepp_50_50} &
		\includegraphics[height=4cm]{z_img_f_stepp_150_50} &
		\includegraphics[height=4cm]{z_img_woo_stepp_50}

@@

\begin{table}[H]
	\caption{Temporal completeness. For each magnitude interval, the completess was computed by the \citet{stepp_1972} method.}
	\begin{tabular}{c c }
		\hline
	\textbf{magnitude} & \textbf{year (Stepp)} \\
		\hline
		3.0 & 1970 \\
		% 3.5 &  	   \\
		4.0 & 1959 \\
		4.5 & 1951 \\
		% 5.0 &      \\
		% 5.5 &  	   \\
		6.0 & 1933 \\
		\hline
	\end{tabular}
	\label{tab:completeness_stepp}
\end{table}

\begin{table}[H]
	\caption{Temporal completeness. For each magnitude interval, the completess comes from \citet{assumpcao_et_al_2014} converted to $M_W$ from $m_b$ following table \ref{tab:guidelines}.}
	\begin{tabular}{c c}
		\hline
	\textbf{magnitude} & \textbf{year (Assumpção)} \\
		\hline
		3.1 & 1980 \\
		4.3 & 1968 \\
		4.8 & 1962 \\
		% 5.0 &      \\
		% 5.5 &  	   \\
		6.0 & 1940 \\
		\hline
	\end{tabular}
	\label{tab:completeness}
\end{table}
